---
title: Chapter 0
output: distill::distill_article
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<style>
.zoomDiv {
  opacity: 0;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  box-shadow: 10px 10px 50px #888888;
  max-height:100%;
}

.zoomImg {
  width: 100%;
}
</style>


<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').css({opacity: '1', width: '55%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'});
    });
  });
</script>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(R.options = list(width = 150))

library(knitr)
source("R/chapter_figs.R")
```
# Introduction

> *The only new thing in the world is the history you don?t know.*
>
> Harry S. Truman, quoted by DavidMcCulloch


```{block, type="chapterprelude"}
#### Synopsis {-}

This book recounts a long history, a broad overview of how, where, and why the
methods of data visualization, so common today, were conceived and developed.
You can think of it as a guided tour of this history, focusing on social and
scientific questions and a developing language of graphics that provided
insights, for both discovery and communication. 
```


```{block, type="chaptercontents"}
#### Chapter topics

* A Long History
* Overview
	+ Re-Visions 
	+ Chronology versus Theme

```

## Selected Figures


## Selected Figures

```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
 do_chapter(0)
```
