---
title: Chapter 1
output: distill::distill_article
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<style>
.zoomDiv {
  opacity: 0;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  box-shadow: 10px 10px 50px #888888;
  max-height:100%;
}

.zoomImg {
  width: 100%;
}
</style>


<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').css({opacity: '1', width: '55%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'});
    });
  });
</script>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(R.options = list(width = 150))

library(knitr)
source("R/chapter_figs.R")
```
# In the Beginning... {#ch01-intro}

> *If you would understand anything, observe its beginning and its development.* __Aristotle, *Metaphysics*__

<div class="chapterprelude">
#### Synopsis {-}
This chapter is an overview of the larger questions and themes that
provide a context for the book. We consider the relations among numerical data, evidence for an argument and graphs,
and then describe some of the pre-history of the visual representation of numbers and the early rise of 
visualization itself. The story continues to the rise of empirical thinking in philosophy and
science around the 16th Century and the concomitant
remarkable development of the visual representation of numbers to communicate quantitative phenomena.
</div>


<div class="chaptercontents">
#### Chapter topics

* Introduction
	+ The Evolution of Pictures
	+ Connecting Data with Pictures
* Seeing the Unexpected
* The Rise of the Graphic Method and Visual Thinking 
* A Golden Age
</div>


## Selected Figures

```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
 do_chapter(1)
```
