---
title: Chapter 4
output: distill::distill_article
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<style>
.zoomDiv {
  opacity: 0;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  box-shadow: 10px 10px 50px #888888;
  max-height:100%;
}

.zoomImg {
  width: 100%;
}
</style>


<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').css({opacity: '1', width: '55%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'});
    });
  });
</script>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(R.options = list(width = 150))

library(knitr)
source("R/chapter_figs.R")
```
# Vital Statistics: William Farr, John Snow and Cholera {#ch04-vital}

<div class="chapterprelude">
#### Synopsis {-}

A short time later, analogous widespread data collection was begun in the United Kingdom, but this
was in the context of social welfare, poverty, public health and sanitation.
From these efforts emerged two new heroes of
data visualization, William Farr and John Snow, who worked independently trying to
understand the causes of several epidemics of cholera and how the disease could
be mitigated.
</div>

<div class="chaptercontents">

* Cholera 
	+ Farr's Diagrams 
	+ Farr's Natural Law of Cholera
	+ The Transcendent Effect of Water

* John Snow on Cholera
	+ The Broad Street Pump
	+ The Neighborhoods Map

* Re-visioning the Broad Street Pump
* Graphical Successes and Failures
	+ The Answer: A Bug
	+ Florence Nightingale's Graphical Success
</div>



## Selected Figures

```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
 do_chapter(4)
```
