---
title: Chapter 5
output: distill::distill_article
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<style>
.zoomDiv {
  opacity: 0;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  box-shadow: 10px 10px 50px #888888;
  max-height:100%;
}

.zoomImg {
  width: 100%;
}
</style>


<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').css({opacity: '1', width: '55%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'});
    });
  });
</script>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(R.options = list(width = 150))

library(knitr)
source("R/chapter_figs.R")
```
# The Big Bang: William Playfair, the Father of Modern Graphics {#ch05-playfair}

<div class="chapterprelude">

#### Synopsis {-}

At the beginning of the 19th Century, nearly all of the modern forms of data graphics--- the pie chart, the line graph of a time series, and the bar chart--- were invented. These key developments were all due to a wily Scot named William Playfair. He can rightly be called the father of modern graphical methods, and it is only a slight stretch to consider his contributions to be the Big Bang of data graphics. 
</div>

<div class="chaptercontents">
#### Chapter contents {-}

* Playfair's Life 
* Playfair's Graphic Contributions
* The First Pie
* Time-Series Line Graphs
	+ Import and Exports	
	+ Playfair's Failure: Problems With Curve-Difference Charts	
	+ England's National Debt
* Bar Charts
	+ Earlier Bar Charts
* Charts Of History
* Ridgeline Plots
* Why Playfair?
* Playfair's legacy
</div>


## Selected Figures

```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
 do_chapter(5)
```
