---
title: Chapter 6
output: distill::distill_article
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<style>
.zoomDiv {
  opacity: 0;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  box-shadow: 10px 10px 50px #888888;
  max-height:100%;
}

.zoomImg {
  width: 100%;
}
</style>


<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').css({opacity: '1', width: '55%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'});
    });
  });
</script>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(R.options = list(width = 150))

library(knitr)
source("R/chapter_figs.R")
```
# The Origin and Development of the Scatterplot {#ch06-scat}

<div class="chapterprelude">
#### Synopsis {-}
Among all the moderns forms of statistical graphics,
the scatterplot may be considered the most versatile,
and generally useful invention in the entire history of statistical
graphics. It is also notable because William Playfair didn't invent it.
This chapter considers why Playfair was unable to think about such things,
and it traces the invention of the scatterplot to the eminent astronomer John F. W. Herschel.
Scatterplots achieved great importance in the work
of Francis Galton [1822--1911] on the heritability of traits.
Galton's work, visualized through statistical diagrams,
became the source of the statistical ideas of correlation and regression and thus most of
modern statistical methods.
</div>

<div class="chaptercontents">

* Early Displays That Were Not Scatterplots
	+ Johann Lambert
	+ Why Not Playfair?
* John F. W. Herschel and the Orbits Of Twin Stars
	+ Herschel's Graphical Impact Factor
* Francis Galton and the Idea Of Correlation
	+ Galton's Elliptical Insight
	+ Another Asymmetry
* Some Remarkable Scatterplots
	+ The Hertzsprung-Russell Diagram
	+ The Phillips Curve
* Spurious Correlations and Causation
* Scatterplot Thinking 
</div>




## Selected Figures

```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
 do_chapter(6)
```
