---
title: Chapter 9
output: distill::distill_article
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<style>
.zoomDiv {
  opacity: 0;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  box-shadow: 10px 10px 50px #888888;
  max-height:100%;
}

.zoomImg {
  width: 100%;
}
</style>


<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').css({opacity: '1', width: '55%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'});
    });
  });
</script>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(R.options = list(width = 150))

library(knitr)
source("R/chapter_figs.R")
```
# Visualizing Time and Space {#ch09-motion}

```{block, type="chapterprelude"}
#### Synopsis {-}
The recent history of data visualization is much harder to characterize because
innovations have been so varied, and have occurred at an accelerated pace and
have appeared across a wider range of disciplines.
Among the many threads that could be traced, two general categories stand out; these have made
data graphics far more powerful and accessible than ever before.
First, graphical methods have become increasingly dynamic and interactive,
capable of showing changes over time by animation and changing the nature of a graph
from a static image to one that a viewer can directly manipulate, zoom or query.
Second, the escape from flatland has been continued, with a variety of new approaches to 
understanding data in ever higher dimensions.
```

```{block, type="chaptercontents"}
* The Laws of Motion 

* The Horse in Motion 
	+ A Trick of the Eye

* 'Etienne-Jules Marey and a Science of Visualizing Time and Motion

	+ La M'ethode Graphique
	+ Chronophotography 

	+ Falling cats

* Computer Graphics Animation 

* Animated Algorithms 

	+ The MDS movie
	+ Color similarity
	+ The Monte Carlo Method
	+ RANDU

* Travels in High-D Space 

	+ Diabetes classification

* Hardware and Software

	+ Software

* Telling stories with Animated Graphics 

```


## Selected Figures

```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
 do_chapter(9)
```
