---
title: Chapter 10
output: distill::distill_article
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<style>
.zoomDiv {
  opacity: 0;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  box-shadow: 10px 10px 50px #888888;
  max-height:100%;
}

.zoomImg {
  width: 100%;
}
</style>


<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').css({opacity: '1', width: '55%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'});
    });
  });
</script>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(R.options = list(width = 150))

library(knitr)
source("R/chapter_figs.R")
```
# Graphs as Poetry {#ch10-poetry}

<div class="chapterprelude">
#### Synopsis {-}
Graphs are justly celebrated for their ability to accurately present phenomena
in a compact way while simultaneously provide their context. If this were all
that they did, their place in scientific history would be secure. But with
suitable data and the right design, they can also convey emotion. Indeed, in
some instances graphs provide an emotional impact that can be likened to that of
poetry. In this chapter we imagine a collaboration between the civil rights
activist W.E.B. DuBois and the canonized graphic designer C. J. Minard to show
The Great Migration of six million African-Americans fleeing the racism and
terror in the post-Confederacy South to the industrial North. The result of this
*gedanken* collaboration provides a vivid example of how we can profit from
studying the past to help solve the problems of the future.
</div>

<div class="chaptercontents">
#### Chapter contents {-}
* Two Plain Graphical Poems
	+ Young Men and Fire
	+ The Kovno Ghetto
* The Graphic Poetry of Charles Joseph Minard
* Using Graphs in a Narrative Argument
* W. E. B. Du Bois
* The Great Migration
	+ A Gedanken Collaboration
* Conclusion 
</div>



## Selected Figures

```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
 do_chapter(10)
```
